---
title: "Thesis_BCI"
author: "Robert Dragon"
date: "2025-11-03"
output: 
  html_document:
    theme: cerulean
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# -------------------------
# Libraries
# -------------------------
library(tidyverse)
library(readxl)
library(lavaan)
library(semTools)
library(semhelpinghands)
library(stringr)
library(knitr)
library(kableExtra)
library(gt)
library(purrr)
library(ggforce)
library(BayesFactor)
library(writexl)
library(semPlot)
library(ggplot2)
library(dplyr)
library(patchwork)
library(gridExtra)

# -------------------------
# Paths (relative)
# -------------------------
# Replace these with your own CSV/Excel in the repo folder
datapath_AG1 <- "data/AG1_results.csv"
datapath_AG2 <- "data/AG2_results.csv"
datapath_AG3 <- "data/AG3_results.csv"
datapath_AG4 <- "data/AG4_results.csv"
french_data_path <- "data/french_results.xlsx"
```
## Overview of Analytical Workflow
This R Markdown document implements the complete statistical analysis workflow for the study. The script first loads and harmonises raw survey data across age groups using a shared preprocessing function, including variable selection, renaming, and reverse coding. Datasets are merged and restricted to participants who completed the full questionnaire. For additional exclusion-related checks review datasets are generated.
Descriptive analyses are conducted in two parts: demographic characteristics with a focus on age distribution, followed by descriptive statistics for all non-demographic study variables. Two confirmatory factor analyses are then estimated to evaluate the proposed measurement models for the outcome constructs behavioural intention (BI), perceived usefulness (PU), and perceived ease of use (PEOU) and for the set of postulated predictor constructs. A structural equation model is subsequently estimated to test the theorised relationships between predictors and behavioural intention, using factor scores for the constructs assumed to act as predictors. Indirect effects are examined in a separate step using bootstrapping to obtain confidence intervals. Finally, behavioural intention in the German sample is compared with the published French sample using a Welch t-test, and pre–post comparisons of perceived usefulness and behavioural intention are conducted using paired-sample t-tests.

## Data Loading and Preprocessing
#### Load data
```{r}
# loading data
data_AG1 <- read.csv(datapath_AG1)
data_AG2 <- read.csv(datapath_AG2)
data_AG3 <- read.csv(datapath_AG3)
data_AG4 <- read.csv(datapath_AG4)

french_data_raw <- read_excel("french_results.xlsx")

```
#### --
#### Prepare all data with one function and merge-in the data sets
```{r}
clean_data <- function(df) {
  df_clean <- df %>% select(
  id,
  startdate,
  datestamp,
  prolific_id = G01Q18,
  prolific_id2 = G01Q05,
  #relationship with technologies
  tec1smartphone = tec1.SQ001.,
  tec1smartwatch = tec1.SQ002.,
  tec1voiceassistants = tec1.SQ003.,
  tec1augmentedreality = tec1.SQ004.,
  tec1virtualreality = tec1.SQ005.,
  tec1autonomicdrive = tec1.SQ006.,
  tec1nonregularly = tec1.SQ007.,
  tec1never = tec1.SQ008.,
  # BCI knowledge
  bek1,
  bek2 = G02Q19.bek2.,
  bek3 = G02Q19.bek3.,
  # General Anxiety / Allgemeine Ängstlichkeit
  all1 = G03Q04.all1.,
  all2 = G03Q04.all2.,
  all3 = G03Q04.all3.,
  all4 = G03Q04.all4.,
  all5 = G03Q04.all5.,
  # attention test 1
  attention7 = G03Q04.SQ009.,
  # Video 1
  has_seen_video1 = G01Q24,
  # Autonomy
  aut1 = G05Q07.aut1.,
  aut2 = G05Q07.aut2.,
  aut3 = G05Q07.aut3.,
  aut4 = G05Q07.aut4.,
  # Subjective Norms
  sub1 = G05Q07.sub1.,
  sub2 = G05Q07.sub2.,
  sub3 = G05Q07.sub3.,
  # Image / Ansehen
  ans1 = G05Q07.ans1.,
  ans2 = G05Q07.ans2.,
  ans3 = G05Q07.ans3.,
  # Computer Anxiety / Ängstlichkeit
  aen1 = G05Q07.aen1.,
  aen2 = G05Q07.aen2.,
  aen3 = G05Q07.aen3.,
  # Visual Aesthetics / Optische Ästhetik
  opt1 = G05Q07.opt1.,
  opt2 = G05Q07.opt2.,
  opt3 = G05Q07.opt3.,
  # Agency / Handlungsfähigkeit
  han1 = G05Q07.han1.,
  han2 = G05Q07.han2.,
  han3 = G05Q07.han3.,
  han4 = G05Q07.han4.,
  # Computer Playfulness / Verspieltheit
  ver1 = G05Q07.ver1.,
  ver2 = G05Q07.ver2.,
  ver3 = G05Q07.ver3.,
  # attention test 2
  attention5 = G05Q07.SQ039.,
  # Ease of Learning / Erlernbarkeit
  erl1 = G05Q07.erl1.,
  erl2 = G05Q07.erl2.,
  erl3 = G05Q07.erl3.,
  erl4 = G05Q07.erl4.,
  # PU1 / Perceived Usefulness 1 (before video2) / Empfundener Nutzen 1
  pu11 = G05Q07.pu11.,
  pu12 = G05Q07.pu12.,
  pu13 = G05Q07.pu13.,
  # PEOU / Perceived Ease of Use / Empfundene Benutzerfreundlichkeit
  peo1 = G05Q07.peo1.,
  peo2 = G05Q07.peo2.,
  peo3 = G05Q07.peo3.,
  # BI1 / Behavioural Intention 1 (before video2) / Handlungsabsichten 1
  bi11 = G05Q07.bi11.,
  bi12 = G05Q07.bi12.,
  bi13 = G05Q07.bi13.,
  bi14 = G05Q07.bi14.,
  # Video 2
  has_seen_video2 = G05Q25,
  # Result Demonstrability / Nachvollziehbarkeit der Ergebnisse
  nac1 = G07Q09.nac1.,
  nac2 = G07Q09.nac2.,
  nac3 = G07Q09.nac3.,
  nac4 = G07Q09.nac4.,
  # Benefits/Risks Ratio / Verhältnis Risiko/Nutzen
  ris1 = G07Q09.ris1.,
  ris2 = G07Q09.ris2.,
  ris3 = G07Q09.ris3.,
  ris4 = G07Q09.ris4.,
  # attention test 3
  attention1 = G07Q09.SQ013.,
  # Relevance / wissenschaftliche Relevanz
  rel1 = G07Q09.rel1.,
  rel2 = G07Q09.rel2.,
  rel3 = G07Q09.rel3.,
  rel4 = G07Q09.rel4.,
  # Self-Efficacy / Selbstwirksamkeit
  sel1,
  # Social Support
  soz1 = G07Q11.soz1.,
  soz2 = G07Q11.soz2.,
  soz3 = G07Q11.soz3.,
  soz4,
  # PU2 / Perceived Usefulness 2 / Empfundener Nutzen 2
  pu21 = G07Q13.pu21.,
  pu22 = G07Q13.pu22.,
  pu23 = G07Q13.pu23.,
  # BI2 / Behavioural Intention 2 / Verhaltensabsichten 2
  bi21 = G07Q13.bi21.,
  bi22 = G07Q13.bi22.,
  bi23 = G07Q13.bi23.,
  bi24 = G07Q13.bi24.,
  # Gender / Geschlecht
  ges1,
  # Age / Alter
  alt1,
  # Education / Bildung
  bil1,
  # Occupation / Beruf
  ber1,
  # Stroke / Schlaganfall
  sch1 = G08Q20.sch1.,
  sch2 = G08Q20.sch2.,
  sch3 = G08Q21.sch3.,
  sch4,
  # stats about how long did they take IIII This looks like it needs to be coded for every age group
  interviewtime,
  time_taken_group_ID = 104,
  time_taken_group_PartInfo = 106,
  time_taken_group_Consent = 108,
  time_taken_group_extraInfo = 111,
  time_taken_group_TechnologyUsage = 113,
  time_taken_group_BCIKnowledge = 115,
  time_taken_group_Factors1 = 118,
  time_taken_group_Video1 = 120,
  time_taken_group_Factors2 = 122,
  time_taken_group_Video2 = 124,
  time_taken_group_Factors3 = 126,
  time_taken_group_SocioDemo = 132
) %>%
  mutate(
    # Reverse-Coding für items die negativ formuliert sind und einen positiv formulierten Faktor messen (oder umgekehrt)
    aut2 = 10 - aut2,
    aut4 = 10 - aut4,
    all3 = 10 - all3,
    all4 = 10 - all4,
    opt3 = 10 - opt3,
    erl2 = 10 - erl2,
    erl4 = 10 - erl4,
    nac4 = 10 - nac4,
    ris1 = 10 - ris1,
    
  )
  
  df_clean
}  

#now applying this function to all four data sets
AG1_clean <- clean_data(data_AG1)
AG2_clean <- clean_data(data_AG2)
AG3_clean <- clean_data(data_AG3)
AG4_clean <- clean_data(data_AG4)

# stacking them together, adding a new column for easier distinguishing age groups later on
data_test_clean_withNA <- bind_rows(
  AG1_clean %>% mutate(AG = "AG1"),
  AG2_clean %>% mutate(AG = "AG2"),
  AG3_clean %>% mutate(AG = "AG3"),
  AG4_clean %>% mutate(AG = "AG4")
)
# keep participants with completed questionnaire
data_test_clean_beforeExclusion <- data_test_clean_withNA %>%
  filter(!is.na(bi24))

##### anonymisation ----

set.seed(123)

anonymized_data <- data_test_clean_beforeExclusion %>%
  slice_sample(prop = 1) %>%        # shuffle rows
  mutate(participant_id = sprintf("P%03d", row_number()))

# create secure key
participant_key <- anonymized_data %>%
  select(participant_id, prolific_id)

# remove identifiers from working dataset
anonymized_data <- anonymized_data %>%
  select(-id, -prolific_id, -prolific_id2, -startdate, -datestamp)
##### end of anonymisation

write.csv(participant_key, "participant_key_secure.csv", row.names = FALSE)


# kick non-completed
data_kicked_out <- data_test_clean_withNA %>%
  filter(is.na(bi24))

# overview of final data sets for each age group; maybe for review purposes
data_AG1_final <- anonymized_data %>%
  filter(AG == "AG1")

data_AG2_final <- anonymized_data %>%
  filter(AG == "AG2")

data_AG3_final <- anonymized_data %>%
  filter(AG == "AG3")

data_AG4_final <- anonymized_data %>%
  filter(AG == "AG4")

####### Preparing French data #######
# French data preparation: getting rid of unnecessary rows, to just have the numbers for BI
french_data <- french_data_raw[-c(1:2), ]
french_BI_items <- c(
  "Q17/4/2_4",
  "Q17/1/2_4",
  "Q17/2/2_4",
  "Q17/2/3_4"
)
french_BI_data <- french_data %>%
  select(all_of(french_BI_items))

french_BI_data <- french_BI_data %>%
  mutate(across(everything(), ~ as.numeric(gsub(",", ".", .x))))

# sanity check
# summary(french_BI_data)


```
#### --

## Code für reviewing purposes

#### --

#### Reviewing purposes#1: creating pdf with histograms for all Participants
```{r}
# quant_vars <- unlist(quant_factors, recursive = TRUE, use.names = FALSE)
# 
# # Create ONE PDF with all participants
# pdf("response_pattern_AG4.pdf", width = 14, height = 6)
# 
# for (i in seq_len(nrow(AG4_clean))) {
# 
# 
#   # Extract participant responses
#   values <- AG4_clean[i, quant_vars] %>%
#     unlist(use.names = TRUE) %>%
#     as.numeric()
# 
#   item_names <- names(values)
# 
#   # Barplot: X = items, Y = response values
#   barplot(
#     values,
#     names.arg = item_names,
#     las = 2,
#     col = "steelblue",
#     border = "grey30",
#     ylim = c(0, 10),
#     main = paste("Participant ID:", participant_id),
#     ylab = "Response Value"
#   )
# }
# 
# dev.off()

```

#### Reviewing purposes#2: creating excel friendly dfs
```{r}

# write_xlsx(AG3_clean,
#            path = file.path(path, "data_AG3_excel_exclusionCheck.xlsx"))

# write_xlsx(AG4_clean,
#            path = file.path(path, "data_AG4_excel_exclusionCheck.xlsx"))
#write_xlsx(data_kicked_out,
#          path = file.path(path, "data_kicked_out.xlsx"))

```
#### --

##### manually excluding participants after exclusion criterias
```{r}
##### manually excluding participants after exclusion criteria

manual_exclude_ids <- c(
  "P026",
  "P010",
  "P130",
  "P174",
  "P033"
)

# store excluded participants
data_manually_excluded <- anonymized_data %>%
  filter(participant_id %in% manual_exclude_ids)

# remove them from dataset
data_test_clean <- anonymized_data %>%
  filter(!participant_id %in% manual_exclude_ids)
```

## Descriptives
#### Demographics
```{r}
# age, gender, education, values per person(/group), stroke
# Convert education (bil1) to numeric (extract years)
data_test_clean <- data_test_clean %>%
  mutate(bil1_num = as.numeric(str_extract(bil1, "\\d+")))

# ---- Numeric summaries ----
age_stats <- data_test_clean %>%
  summarise(
    Mean = mean(alt1, na.rm = TRUE),
    SD = sd(alt1, na.rm = TRUE),
    Median = median(alt1, na.rm = TRUE),
    Min = min(alt1, na.rm = TRUE),
    Max = max(alt1, na.rm = TRUE)
  )

edu_stats <- data_test_clean %>%
  summarise(
    Mean = mean(bil1_num, na.rm = TRUE),
    SD = sd(bil1_num, na.rm = TRUE),
    Median = median(bil1_num, na.rm = TRUE),
    Min = min(bil1_num, na.rm = TRUE),
    Max = max(bil1_num, na.rm = TRUE)
  )

# ---- Categorical summaries ----
gender_stats <- data_test_clean %>%
  count(ges1) %>%
  mutate(Percent = round(100 * n / sum(n), 1))

stroke_stats <- data_test_clean %>%
  count(sch1) %>%
  mutate(Percent = round(100 * n / sum(n), 1))

# ---- Build table blocks ----
age_table <- tibble(
  Variable = "Age (years)",
  `Category / Statistic` = c("Mean (SD)", "Median [Min–Max]"),
  Value = c(
    sprintf("%.2f (%.2f)", age_stats$Mean, age_stats$SD),
    sprintf(
      "%d [%d–%d]",
      as.integer(age_stats$Median),
      as.integer(age_stats$Min),
      as.integer(age_stats$Max)
    )
  )
)

edu_table <- tibble(
  Variable = "Education (years)",
  `Category / Statistic` = c("Mean (SD)", "Median [Min–Max]"),
  Value = c(
    sprintf("%.2f (%.2f)", edu_stats$Mean, edu_stats$SD),
    sprintf(
      "%d [%d–%d]",
      as.integer(edu_stats$Median),
      as.integer(edu_stats$Min),
      as.integer(edu_stats$Max)
    )
  )
)

gender_table <- gender_stats %>%
  mutate(
    Variable = "Gender",
    `Category / Statistic` = ges1,
    Value = sprintf("%d (%.1f%%)", n, Percent)
  ) %>%
  select(Variable, `Category / Statistic`, Value)

stroke_table <- stroke_stats %>%
  mutate(
    Variable = "Stroke history",
    `Category / Statistic` = sch1,
    Value = sprintf("%d (%.1f%%)", n, Percent)
  ) %>%
  select(Variable, `Category / Statistic`, Value)

# ---- Combine everything ----
descriptive_table <- bind_rows(
  age_table,
  edu_table,
  gender_table,
  stroke_table
)

# ---- Print publication-ready table ----
kable(
  descriptive_table,
  caption = "Descriptive characteristics of the sample",
  align = c("l", "l", "r")
) %>%
  kable_styling(
    bootstrap_options = "striped",
    full_width = FALSE
  )
```

#### Age table just for comparison with representative goals
```{r}
# ---- Step 1: Define age groups in data ----
data_test_clean <- data_test_clean %>%
  mutate(
    age_group = case_when(
      alt1 >= 18 & alt1 <= 29 ~ "18–29 years",
      alt1 >= 30 & alt1 <= 49 ~ "30–49 years",
      alt1 >= 50 & alt1 <= 64 ~ "50–64 years",
      alt1 >= 65              ~ "65+ years",
      TRUE ~ NA_character_
    )
  )

# ---- Step 2: Objective values (Destatis 2022, target N = 588) ----
objective_table <- tibble(
  age_group = c("18–29 years", "30–49 years", "50–64 years", "65+ years"),
  Objective_Percent = c(15.51, 30.27, 27.54, 26.69),
  Objective_N = c(88, 173, 157, 152)
)

# ---- Step 3: Obtained values from data ----
obtained_table <- data_test_clean %>%
  filter(!is.na(age_group)) %>%
  count(age_group) %>%
  mutate(
    Obtained_N = n,
    Obtained_Percent = round(100 * n / sum(n), 2)
  ) %>%
  select(age_group, Obtained_Percent, Obtained_N)

# ---- Step 4: Combine objective and obtained ----
age_comparison_table <- objective_table %>%
  left_join(obtained_table, by = "age_group")

# ---- Step 5: Pretty output ----
kable(
  age_comparison_table,
  col.names = c(
    "Age group",
    "Objective (%)",
    "Objective N",
    "Obtained (%)",
    "Obtained N"
  ),
  caption = "Comparison of planned and obtained age distribution of the sample"
) %>%
  kable_styling(
    bootstrap_options = c("striped"),
    full_width = FALSE,
    position = "center"
  )
```

#### mean and sd of interviewtime
```{r}
# Overall statistics
overall_stats <- data_test_clean %>%
  summarise(
    N_total = n(),
    mean_sec = mean(interviewtime, na.rm = TRUE),
    sd_sec = sd(interviewtime, na.rm = TRUE),
    mean_min = mean_sec / 60,
    sd_min = sd_sec / 60
  )

# Statistics by age group
group_stats <- data_test_clean %>%
  group_by(AG) %>%
  summarise(
    n = n(),
    mean_sec = mean(interviewtime, na.rm = TRUE),
    sd_sec = sd(interviewtime, na.rm = TRUE),
    mean_min = mean_sec / 60,
    sd_min = sd_sec / 60
  )

# Print results
overall_stats
group_stats
```

#### Descriptives for all the non-demografics (all the quantitative and categorical factors)
```{r}
# --- 1️⃣ Quantitative factors setup ---
quant_factors <- list(
  `Target factors` = list(
    BI1 = c("bi11","bi12","bi13","bi14"),
    BI2 = c("bi21","bi22","bi23","bi24"),
    PU1 = c("pu11","pu12","pu13"),
    PU2 = c("pu21","pu22","pu23"),
    PEOU = c("peo1","peo2","peo3")
  ),
  `System characteristics` = list(
    Relevance = c("rel1","rel2","rel3","rel4"),
    `Benefits/Risks` = c("ris1","ris2","ris3","ris4"),
    `Result demonstrability` = c("nac1","nac2","nac3","nac4"),
    `Visual aesthetics` = c("opt1","opt2","opt3"),
    Image = c("ans1","ans2","ans3")
  ),
  `Social influence` = list(
    `Subjective norm` = c("sub1","sub2","sub3")
  ),
  `Individuals differences` = list(
    Autonomy = c("aut1","aut2","aut3","aut4"),
    `General anxiety` = c("all1","all2","all3","all4","all5"),
    `Computer anxiety` = c("aen1","aen2","aen3")
  ),
  `Facilitating conditions` = list(
    Agency = c("han1","han2","han3","han4"),
    `Computer playfulness` = c("ver1","ver2","ver3"),
    `Ease of learning` = c("erl1","erl2","erl3","erl4"),
    `Social support` = c("soz1","soz2","soz3")
  )
)

# Compute factor scores
for(cat in names(quant_factors)){
  for(fac in names(quant_factors[[cat]])){
    items <- quant_factors[[cat]][[fac]]
    score_name <- paste0(fac, "_score")
    data_test_clean[[score_name]] <- rowMeans(data_test_clean[items], na.rm = TRUE)
  }
}

# Build quantitative table with category subtitles, no asterisks
quant_table <- map_dfr(names(quant_factors), function(cat){
  tibble(
    Factor = c(cat, names(quant_factors[[cat]])),  # category as plain text
    Mean = c("", sapply(names(quant_factors[[cat]]), function(fac){
      round(mean(data_test_clean[[paste0(fac, "_score")]], na.rm = TRUE), 2)
    })),
    SD = c("", sapply(names(quant_factors[[cat]]), function(fac){
      round(sd(data_test_clean[[paste0(fac, "_score")]], na.rm = TRUE), 2)
    }))
  )
})

# Print table
kable(quant_table, caption = "Descriptive statistics for quantitative factors") %>%
  kable_styling(full_width = FALSE, position = "center", font_size = 12)

# --- Define categorical factors and their answer options ---

# --- Define categorical factors and answer options (German) ---
cat_factors <- list(
  "Use of technologies" = c(
    "Smartphone",
    "Smartwatch",
    "Sprachgesteuerte Assistenten",
    "Augmented Reality-Tools",
    "Virtual Reality-Tools",
    "Autonomes Fahrzeug",
    "Ich verwende diese Technologien nur gelegentlich",
    "Ich verwende diese Technologien nie"
  ),
  "BCI knowledge" = c(
    "Ich möchte nicht antworten",
    "Nein",
    "Ja, aber ich habe noch nie eine Gehirn-Computer-Schnittstelle genutzt",
    "Ja, und ich habe bereits einmal eine Gehirn-Computer-Schnittstelle genutzt",
    "Ja, und ich habe eine Gehirn-Computer-Schnittstelle 2- bis 5-mal genutzt",
    "Ja, und ich habe eine Gehirn-Computer-Schnittstelle mehr als 5-mal genutzt"
  ),
  "Self-efficacy" = c(
    "Allein und unabhängig.",
    "Allein, sofern eine Unterstützungsfunktion in das System integriert ist um Hilfe zu bekommen, zum Beispiel in Form eines virtuellen Begleiters.",
    "Allein, sofern ich eine ähnliche Technologie schon einmal benutzt habe.",
    "Nur, wenn mir jemand zeigt, wie ich die Übungen durchführen kann und mich nach und nach anleitet."
  ),
  "Social support" = c(
    "Selbstständig, allein zu Hause.",
    "Allein, aber in einer Gesundheitseinrichtung.",
    "In Anwesenheit einer medizinischen Fachkraft."
  )
)

# --- Mapping dataset columns ---
mapping <- list(
  "Use of technologies" = c(
    "Smartphone" = "tec1smartphone",
    "Smartwatch" = "tec1smartwatch",
    "Sprachgesteuerte Assistenten" = "tec1voiceassistants",
    "Augmented Reality-Tools" = "tec1augmentedreality",
    "Virtual Reality-Tools" = "tec1virtualreality",
    "Autonomes Fahrzeug" = "tec1autonomicdrive",
    "Ich verwende diese Technologien nur gelegentlich" = "tec1nonregularly",
    "Ich verwende diese Technologien nie" = "tec1never"
  ),
  "BCI knowledge" = "bek1",
  "Self-efficacy" = "sel1",
  "Social support" = "soz4"
)

# --- Choice type labels ---
choice_type <- c(
  "Use of technologies" = "Multiple choice",
  "BCI knowledge" = "Single choice",
  "Self-efficacy" = "Single choice",
  "Social support" = "Single choice"
)

# --- Compute percentages ---
cat_table_list <- list()

for(fac in names(cat_factors)){
  
  answers <- cat_factors[[fac]]
  
  perc_values <- sapply(answers, function(a){
    
    if(fac == "Use of technologies"){
      # Multiple choice: count "Ja"
      col_name <- mapping[[fac]][a]
      perc <- round(
        100 * sum(data_test_clean[[col_name]] == "Ja", na.rm = TRUE) / nrow(data_test_clean),
        1
      )
      
    } else {
      # Single choice
      col_name <- mapping[[fac]]
      perc <- round(
        100 * sum(data_test_clean[[col_name]] == a, na.rm = TRUE) / nrow(data_test_clean),
        1
      )
    }
    
    paste0(a, " (", perc, "%)")
  })
  
  # Combine answers into one clean line
  answers_combined <- paste(perc_values, collapse = "; ")
  
  # Store row
  cat_table_list[[fac]] <- tibble(
    Factor = paste0(fac, " (", choice_type[fac], ")"),
    `Answer options` = answers_combined
  )
}

# --- Bind rows ---
cat_summary <- bind_rows(cat_table_list)

# --- Print publication-ready table ---
kable(
  cat_summary,
  caption = "Descriptive statistics for categorical factors"
) %>%
  kable_styling(
    full_width = FALSE,
    position = "center",
    font_size = 12
  ) %>%
  column_spec(2, width = "16cm")
```

## Statistical Analysis
#### CFA 1
```{r}
modelA_cfa1 <- '
# Latente Variablen: Target Factors
BI =~ bi21 + bi22 + bi23 + bi24
PU =~ pu21 + pu22 + pu23
PEOU =~ peo1 + peo2 + peo3
'

fitA <- cfa(
  modelA_cfa1,
  data = data_test_clean,
  std.lv = TRUE    # fix latent variances to 1 (this enables to use that output for creating the latent scores). Here this is not needed but added for consistency
  )

# check fit
summary(fitA, fit.measures = TRUE, standardized = TRUE)

# McDonald’s ω
compRelSEM(fitA)
#mcD <- compRelSEM(fitA)
#mcD

```
##### plotting CFA 1
```{r}
pdf("CFA_ModelA.pdf", width = 10, height = 7)  # width and height in inches

semPaths(
  fitA,
  what = "std",
  whatLabels = "std",
  style = "lisrel",
  layout = "tree2",
  rotation = 1,
  
  residuals = FALSE,
  intercepts = FALSE,
  exoCov = TRUE,
  
  sizeLat = 9,
  sizeMan = 7,
  
  edge.width = 0.8,
  edge.color = "black",
  
  label.cex = 1.0,
  edge.label.cex = 0.9,
  
  nCharNodes = 0
)

dev.off()
```

#### CFA 2
```{r}
modelB_cfa2 <- '
# Latente Variablen: Predictor Factors
Relevance =~ rel1 + rel2 + rel3 + rel4
Benefits_Risks =~ ris1 + ris2 + ris3 + ris4
Result_Demonstrability =~ nac1 + nac2 + nac3 + nac4
Autonomy =~ aut1 + aut2 + aut3 + aut4
General_Anxiety =~ all1 + all2 + all3 + all4 + all5
Subjective_Norms =~ sub1 + sub2 + sub3
Image =~ ans1 + ans2 + ans3
Computer_Anxiety =~ aen1 + aen2 + aen3
Visual_Aesthetics =~ opt1 + opt2 + opt3
Agency =~ han1 + han2 + han3 + han4
Playfulness =~ ver1 + ver2 + ver3
Ease_of_Learning =~ erl1 + erl2 + erl3 + erl4
# note to myself! its just 47 items, one soz-item (soz4) is not being assessed via the slider and is qualitative!
Social_Support =~ soz1 + soz2 + soz3

'

fitB <- cfa(
  modelB_cfa2, 
  data = data_test_clean,
  std.lv = TRUE     # fix latent variances to 1 (this enables to use that output for creating the latent scores). 
                    # std.lv = TRUE ensures: Latent variables are on the same standardized scale. Factor scores can be interpreted as z-scores
                    # lavaan will treat those scores as observed variables in the SEM
  )
summary(fitB, fit.measures = TRUE, standardized = TRUE)

# McDonald’s ω
compRelSEM(fitB)
```

#### SEM
```{r}
# Preparation for the SEM. The predictor factors will be included in the model as their latent scores!
# Extract factor scores for SEM
scoresB <- lavPredict(fitB, method = "regression")
head(scoresB)

# Add latent predictor scores to main dataset
data_sem <- cbind(data_test_clean, scoresB)

# Check
# head(data_sem)

modelC_sem <- '
# --- Latent variables ---
BI  =~ bi21 + bi22 + bi23 + bi24
PU  =~ pu21 + pu22 + pu23
PEOU =~ peo1 + peo2 + peo3

# --- Regressions with labels ---
# Direct effects
BI ~ b1*PU + b2*PEOU + b3*Subjective_Norms
PU ~ a1*PEOU + a2*Relevance + a3*Benefits_Risks + a4*Result_Demonstrability +
      a5*Visual_Aesthetics + a6*Image + a7*Subjective_Norms +
      a8*General_Anxiety + a9*Computer_Anxiety + a10*Autonomy
PEOU ~ c1*General_Anxiety + c2*Computer_Anxiety + c3*Autonomy +
        c4*Agency + c5*Playfulness + c6*Ease_of_Learning + c7*Social_Support

# --- Indirect effects via PU ---
rel_bi_via_pu   := a2  * b1   # Relevance
ris_bi_via_pu   := a3  * b1   # Benefits / Risks
nac_bi_via_pu   := a4  * b1   # Result demonstrability
opt_bi_via_pu   := a5  * b1   # Visual aesthetics
ans_bi_via_pu   := a6  * b1   # Image
sub_bi_via_pu   := a7  * b1   # Subjective norm
all_bi_via_pu   := a8  * b1   # General anxiety
aen_bi_via_pu   := a9  * b1   # Computer anxiety
aut_bi_via_pu   := a10 * b1   # Autonomy
peou_bi_via_pu  := a1  * b1   # PEOU → PU → BI

# --- Indirect effects via PEOU ---
all_bi_via_peou := c1 * b2    # General anxiety
aen_bi_via_peou := c2 * b2    # Computer anxiety
aut_bi_via_peou := c3 * b2    # Autonomy
han_bi_via_peou := c4 * b2    # Agency
ver_bi_via_peou := c5 * b2    # Computer playfulness
erl_bi_via_peou := c6 * b2    # Ease of learning
soz_bi_via_peou := c7 * b2    # Social support
'

fitC <- sem(modelC_sem, data = data_sem)
summary(fitC, fit.measures = TRUE, standardized = TRUE)
```

#### SEM with bootstrapping for direct and indirect effects
```{r}
# Fit SEM with 5000 bootstrap samples
fitC_boot <- sem(
  modelC_sem,
  data = data_sem,
  se = "bootstrap",
  bootstrap = 5000
)

# # Trigger internal parameter bookkeeping to avoid est1 error
# parameterEstimates(fitC_boot, standardized = TRUE)

# Standard summary with bootstrap CIs
summary(
  fitC_boot,
  standardized = TRUE,
  ci = TRUE
)


# using the extra package for SEM: using this function to get standardized solution with bootstrap CIs
ci_boot <- standardizedSolution_boot_ci(fitC_boot)
# Print the results
print(ci_boot, output = "text")

# prob wrong use/failed the knit/unneccessary?
# # same, but just for BI (what we are interested in)
# ci_boot_BI <- subset(ci_boot, lhs == "BI")
# print(ci_boot_BI, output = "text")


# Parameter estimates with bootstrap CIs (includes indirect effects)
# pe_boot <- parameterEstimates(
#   fitC_boot,
#   standardized = TRUE,
#   ci = TRUE,
#   level = 0.95
# )
# 
# # Extract indirect effects only
# pe_indirect <- subset(pe_boot, op == ":=")
# 
# # Print all indirect effects
# kable(
#   pe_indirect,
#   digits = 3,
#   caption = "Bootstrapped indirect effects with 95% confidence intervals"
# ) %>%
#   kable_styling(full_width = FALSE)
```
##### print SEM as pdf
```{r}
# Save SEM path diagram to PDF
pdf("SEM_ModelC.pdf", width = 10, height = 7)  # adjust width/height

semPaths(
  fitC_boot,               
  what = "std",            # standardized solution
  whatLabels = "std",      # show standardized coefficients on edges
  style = "lisrel",        # clean LISREL-style boxes
  layout = "tree2",        # hierarchical, top-down layout
  rotation = 1,            # adjust node rotation for clarity

  residuals = FALSE,       # hide residuals
  intercepts = FALSE,      # hide intercepts
  exoCov = FALSE,          # do NOT show exogenous covariances

  sizeLat = 9,             # latent variable box size
  sizeMan = 7,             # observed variable box size

  edge.width = 0.8,        # thickness of arrows
  edge.color = "black",    # arrow color

  label.cex = 1.0,         # size of node labels
  edge.label.cex = 0.9,    # size of edge labels

  nCharNodes = 0           # no truncation of node labels
)

dev.off()
```



#### Comparing BI-scores between Germany-sample and France-sample
```{r}
# Compute German BI mean per participant
data_test_clean$BI_mean <- rowMeans(
  data_test_clean[, c("bi21", "bi22", "bi23", "bi24")],
  na.rm = TRUE
)
# Compute French BI mean per participant
french_BI <- rowMeans(french_BI_data, na.rm = TRUE)
french_BI <- french_BI[!is.na(french_BI)]

# sum(is.na(data_test_clean$BI_mean))  # German sample
# sum(is.na(french_BI))                # French sample

# Welch two-sample t-test
welch_test_result <- t.test(
  data_test_clean$BI_mean,
  french_BI,
  alternative = "two.sided",  # two-sided test
  var.equal = FALSE           # Welch, allows unequal variances
)

welch_test_result
# if p ≥ .05 → no significant difference

# "In addition, we will conduct a Bayesian independent-samples t-test to assess the evidence for or against 
# a difference between samples. Bayes factors will be used to distinguish between absence of evidence 
# and evidence for no difference, with BF₀₁ ≥ 3 interpreted as evidence in favour of no difference between 
# samples. 

# Bayesian t-test
bf_result <- ttestBF(
  x = data_test_clean$BI_mean,
  y = french_BI,
  paired = FALSE
)

bf_result
# Extract numeric BF10
bf10 <- extractBF(bf_result, onlybf = TRUE)
bf10
#> e.g., 0.1506

# Compute BF01 (evidence for H0)
bf01 <- 1 / bf10
bf01
if (bf01 >= 3) {
  message("BF01 = ", round(bf01, 2), 
          ": evidence in favor of no difference (supports H0, as BF₀₁ ≥ 3 ).")
}
```

##### plotting welch - FR/GER BI
```{r}
# Combine German and French BI into one dataframe
plot_data <- tibble(
  BI = c(data_test_clean$BI_mean, french_BI),
  Group = rep(c("Germany", "France"),
              c(nrow(data_test_clean), length(french_BI)))
)

# Define thesis-consistent colors instead of flag colors
# Germany: light cyan fill, medium blue outline
# France: slightly different light cyan fill, darker blue outline
group_colors <- tibble(
  Group = c("Germany", "France"),
  fill_color = c("#E0F0FA", "#E0F0FA"),
  outline_color = c("#6699CC", "#6699CC")
)

# Join colors with plot_data
plot_data <- plot_data %>%
  left_join(group_colors, by = "Group")

# Compute summary statistics
summary_data <- plot_data %>%
  group_by(Group) %>%
  summarize(
    mean_BI = mean(BI),
    sd_BI = sd(BI),
    n = n(),
    ci_lower = mean_BI - qt(0.975, n-1) * sd_BI / sqrt(n),
    ci_upper = mean_BI + qt(0.975, n-1) * sd_BI / sqrt(n)
  ) %>%
  left_join(group_colors, by = "Group")

# Extract stats for annotation
t_val <- round(welch_test_result$statistic, 2)
p_val <- round(welch_test_result$p.value, 3)
bf_val <- round(bf01, 2)

# Plot
ggplot() +
  # Individual points colored by outline
  geom_jitter(
    data = plot_data,
    aes(x = Group, y = BI),
    width = 0.15, height = 0,
    alpha = 0.4, size = 3,
    color = plot_data$outline_color
  ) +
  # Mean points in black for clarity
  geom_point(
    data = summary_data,
    aes(x = Group, y = mean_BI),
    size = 5, color = "black"
  ) +
  # Add mean value labels above black dots
  geom_text(
    data = summary_data,
    aes(x = Group, y = mean_BI, 
        label = round(mean_BI, 2)),
    vjust = -1.2,      # moves text above the dot
    size = 5,
    fontface = "bold"
  ) +
  # 95% CI error bars
  geom_errorbar(
    data = summary_data,
    aes(x = Group, ymin = ci_lower, ymax = ci_upper),
    width = 0.2, linewidth = 1, color = "black"
  ) +
  # Dashed line connecting means
  geom_line(
    data = summary_data,
    aes(x = Group, y = mean_BI, group = 1),
    # linetype = "dashed",
    linewidth = 0.8, color = "black"
  ) +
  # Annotate p-value and BF01
  # annotate(
  #   "text",
  #   x = 1.5,
  #   y = 3.7,
  #   label = paste0("t = ", t_val, ", p = ", p_val, "\nBF01 = ", bf_val),
  #   size = 4,
  #   vjust = 1
  # ) +
  theme_minimal(base_size = 14) +
  labs(
    
    x = "Sample",
    y = "BI Score"
  ) +
  theme(
  axis.text.x = element_text(face = "bold"),  
  legend.position = "none",
  panel.grid.major.x = element_blank(),
  panel.grid.minor.x = element_blank()
) +
  scale_y_continuous(
    limits = c(0, 10),
    breaks = c(0, 2.5, 5, 7.5, 10)
  )

ggsave(
  filename = "BI_FR_GER_Welch.pdf",
  width = 8,
  height = 6,
  units = "in"
)

## getting the SD's for reporting in thesis
cat("German sample SD:", summary_data$sd_BI[summary_data$Group == "Germany"], "\n")
cat("French sample SD:", summary_data$sd_BI[summary_data$Group == "France"], "\n")
```

#### Comparing BI and PU with pre and post video2 values
```{r}
# Compute pre- and post-video means for PU
data_test_clean$PU_pre_mean  <- rowMeans(data_test_clean[, c("pu11", "pu12", "pu13")], na.rm = TRUE)
data_test_clean$PU_post_mean <- rowMeans(data_test_clean[, c("pu21", "pu22", "pu23")], na.rm = TRUE)

# Compute pre- and post-video means for BI
data_test_clean$BI_pre_mean  <- rowMeans(data_test_clean[, c("bi11", "bi12", "bi13", "bi14")], na.rm = TRUE)
data_test_clean$BI_post_mean <- rowMeans(data_test_clean[, c("bi21", "bi22", "bi23", "bi24")], na.rm = TRUE)

# One-sided paired t-test: PU post > PU pre
t_test_PU <- t.test(
  data_test_clean$PU_post_mean,
  data_test_clean$PU_pre_mean,
  paired = TRUE,
  alternative = "greater"
)

# One-sided paired t-test: BI post > BI pre
t_test_BI <- t.test(
  data_test_clean$BI_post_mean,
  data_test_clean$BI_pre_mean,
  paired = TRUE,
  alternative = "greater"
)

t_test_PU
t_test_BI

# Interpretation for PU
if (t_test_PU$p.value < 0.05) {
  message("PU: Post-video mean is significantly greater than pre-video mean (p = ", 
          signif(t_test_PU$p.value, 3), 
          ", mean difference = ", round(t_test_PU$estimate, 3), ").")
} else {
  message("PU: No significant increase from pre- to post-video (p = ", 
          signif(t_test_PU$p.value, 3), ").")
}

# Interpretation for BI
if (t_test_BI$p.value < 0.05) {
  message("BI: Post-video mean is significantly greater than pre-video mean (p = ", 
          signif(t_test_BI$p.value, 3), 
          ", mean difference = ", round(t_test_BI$estimate, 3), ").")
} else {
  message("BI: No significant increase from pre- to post-video (p = ", 
          signif(t_test_BI$p.value, 3), ").")
}
```

```{r}
# ----------------------------
# Prepare data
# ----------------------------
plot_data <- data_test_clean %>%
  select(participant_id, BI_pre_mean, BI_post_mean, PU_pre_mean, PU_post_mean) %>%
  pivot_longer(
    cols = -participant_id,
    names_to = c("Variable", "Time"),
    names_pattern = "(BI|PU)_(pre|post)_mean",
    values_to = "Score"
  ) %>%
  mutate(
    Time = recode(Time, pre = "Pre-video", post = "Post-video"),
  )

# ----------------------------
# Function to make paired plots with colored lines
# ----------------------------
paired_plot_colored <- function(var_name, color="#6699CC") {
  data_subset <- plot_data %>% filter(Variable == var_name)
  
  summary_data <- data_subset %>%
    group_by(Time) %>%
    summarise(
      Mean = mean(Score, na.rm = TRUE),
      SD = sd(Score, na.rm = TRUE),
      N = sum(!is.na(Score)),
      SE = SD / sqrt(N),
      .groups = "drop"
    )
  
  ggplot(data_subset, aes(x = Time, y = Score, group = participant_id)) +
    # participant lines
    geom_line(color = color, alpha = 0.4) +
    geom_point(color = color, alpha = 0.4) +
    # mean line in black
    geom_line(data = summary_data, aes(x = Time, y = Mean, group = 1),
              color = "#333333", size = 1.5) +
    # mean points in black
    geom_point(data = summary_data, aes(x = Time, y = Mean),
               color = "#333333", size = 4, inherit.aes = FALSE) +
    # error bars in black
    geom_errorbar(data = summary_data,
                  aes(x = Time, ymin = Mean - SE, ymax = Mean + SE),
                  width = 0.2, color = "#333333", size = 1, inherit.aes = FALSE) +
    # # mean value labels
    # geom_text(data = summary_data,
    #           aes(x = Time, y = Mean, label = round(Mean, 2)),
    #           vjust = -0.5,
    #           color = "black",
    #           size = 4,
    #           fontface = "bold",
    #           inherit.aes = FALSE) +
    # axes
    scale_x_discrete(limits = c("Pre-video", "Post-video")) +
    scale_y_continuous(
      limits = c(0, 10),
      breaks = seq(0, 10, by = 2.5),
      expand = c(0, 0)
    ) +
    labs(title = var_name,
     y = "Score", x = "Time") +
theme_minimal(base_size = 14) +
theme(plot.title = element_text(hjust = 0.5))
}

# ----------------------------
# Create individual plots
# ----------------------------
bi_plot <- paired_plot_colored("BI", color="#6699CC")
pu_plot <- paired_plot_colored("PU", color="#C08081")

# ----------------------------
# Combine them side by side
# ----------------------------
combined_plot <- bi_plot + pu_plot + plot_layout(ncol = 2, widths = c(1, 1))

# ----------------------------
# Display the combined plot
# ----------------------------
combined_plot

# Save combined plot as PDF
ggsave(
  filename = "BI_PU_pre_post_plot.pdf",  # file name
  plot = combined_plot,                  
  width = 10,                            # width in inches
  height = 5,                            # height in inches
  units = "in",                          # units for width/height
  device = "pdf"                         # save as PDF
)
# View the SEs
summary_stats <- plot_data %>%
  group_by(Variable, Time) %>%
  summarise(
    Mean = mean(Score, na.rm = TRUE),
    SD = sd(Score, na.rm = TRUE),
    N = sum(!is.na(Score)),
    SE = SD / sqrt(N),
    .groups = "drop"
  )
summary_stats %>% select(Variable, Time, Mean, SD, SE)
```

```{r}
# Compute standard errors for BI and PU pre- and post-video for figure description
se_table <- plot_data %>%
  group_by(Variable, Time) %>%
  summarise(
    N = sum(!is.na(Score)),
    SD = sd(Score, na.rm = TRUE),
    SE = SD / sqrt(N),
    .groups = "drop"
  ) %>%
  select(Variable, Time, SE)

se_table
```

##### Full print for appendices of all fit indices (chi,CFI, TLI, SRMR, RMSEA)
```{r}
# Function to save fit indices as PDF
save_fit_pdf <- function(fit, model_name, file_name) {
  # Extract key fit indices
  fit_indices <- fitMeasures(fit, c("chisq","df","pvalue","cfi","tli","rmsea","srmr"))
  fit_df <- data.frame(
    Index = c("Chi-Square", "Degrees of Freedom", "p-value", 
              "CFI", "TLI", "RMSEA", "SRMR"),
    Value = round(fit_indices, 3)
  )
  
  # Create PDF
  pdf(file_name, width = 6, height = 4)  # adjust size as needed
  grid.table(fit_df, rows = NULL)
  dev.off()
  
  cat(paste("PDF saved as", file_name, "\n"))
}

# Save each model's fit indices as a separate PDF
save_fit_pdf(fitA, "CFA 1 (fitA)", "fitA_indices.pdf")
save_fit_pdf(fitB, "CFA 2 (fitB)", "fitB_indices.pdf")
save_fit_pdf(fitC, "SEM (fitC)", "fitC_indices.pdf")
```